---
title       : Introduction To The National Park Trip Planner
subtitle    : 
author      : Taisong Jing
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

## Motivation

It is always exciting to have vacations at the tremendously gorgeous national parks in the U.S., especially when we are talking about the 25 national parks in the Southwest and California:

[http://parks.mapquest.com/national-parks/map-of-all-national-parks](http://parks.mapquest.com/national-parks/map-of-all-national-parks)

Got scared when you tried to plan your trip among the clustered national parks? Our **National Park Trip Planner** will solve the problem for you in a minute, possibly with surprising bonus visits on the way!

--- 

## A user guide to the trip planner

### What you can do:

- select the national parks as your origin and destination from a list menu

- set with a slider the extra percentage (from 0% to 25%) of distance you are willing to take in order to visit other parks on the way 

### What you can get:

- The shortest distance betwen the origin and the destination

- Other alternative trip plans which may take longer distance but with the oppurtunities to visit more national parks during the journey

---

## R package: {igraph}

The optimization problem behind this trip planner is to find the k shortest paths between two vertices on an undirected weighted graph. We use the R package **igraph** to implement the algorithms on graphs. 

The following code will produce a graph *g* with 7 vertices and 8 edges and given weights

```{r}{Create graph}
library(igraph)
g<-graph.empty(directed=FALSE)
g<-g+vertices(letters[1:7]) + edges("a","b","a","d","b","c","b","e","c","d","c","g","d","f")
E(g)$weight<-c(1,2,3,4,6,7,8)
```

When k=1, it amounts to find the shortest path and its length between any two given vertices. There is a function *get.shortest.paths* in **igraph** to implemen a variety of algorithms (e.g., Dijkstra algorithm) to find this path. The following example code finds the shortest paths and its length between the vertices "a" and "g" on the graph

---
## Algorithm

```{r}{Shortest path}
vertexsequence<-get.shortest.paths(g,"a","g")$vpath[[1]] #the vertex sequence is in the format of numbers
V(g)$name[vertexsequence] #this converts the numbers into the names of the vertices
as.numeric(shortest.paths(g,"a","g")) #the length of this shortest path
```

When k>1, we implement Yen's algorithm (Yen, Jin Y. (1970)) to find the k shortest paths on the graph. The idea is dynamic programming: remove parts of the previously found shortest paths to find candidates of the next shortest path. 

## That's the mechanism behind how you get the amazing trip recommendations!




